Parsing Postfix log files

### 2009-03-10 doc/logparser-implementation.tex
Some minor changes.

    \item [Classify words based on their frequency]  The frequency of every
        tuple \texttt{(word, word's position within the log line)} is
        checked: if its frequency is greater than the threshold supplied by
        the user (1\% of all log lines is generally a good starting point)
        it is classified as a fixed word, otherwise it is classified as a
        variable term.  If a variable term appears sufficiently often it
        will be misclassified as a fixed term, but that should be noticed
        by the user when reviewing the new regexes.  Variable terms are
        replaced by \texttt{.+}, which means to match zero or more of any
        character.  XXX SHOULD I USE \verb![\S]+! INSTEAD\@?

@@

@@

XXX MAYBE FIND OUT WHAT CLIENTS DISCONNECT\@?  Some mail clients disconnect
abruptly if a second or subsequent recipient is rejected; they may also
disconnect after other errors, but such disconnections are either
unimportant or are handled elsewhere in the parser
(\sectionref{timeouts-during-data-phase}).  Sadly, Postfix does not log a
message saying the mail has been discarded, as should be expected by now.
The checks to identify this happening are:

@@

    \item The hostname used in the HELO command is not logged if the mail
        is accepted.\footnote{Tested with Postfix 2.2.10, 2.3.11, and
        2.4.7; this may possibly have changed in Postfix 2.5.  XXX TEST
        THIS AGAIN.}  Rectifying this is relatively simple: create a
        restriction that is guaranteed to warn for every accepted mail, as
        follows:

>>>>

    \item [Classify words based on their frequency]  The frequency of every
        tuple \texttt{(word, word's position within the log line)} is
        checked: if its frequency is greater than the threshold supplied by
        the user (1\% of all log lines is generally a good starting point)
        it is classified as a fixed word, otherwise it is classified as a
        variable term.  If a variable term appears sufficiently often it
        will be misclassified as a fixed term, but that should be noticed
        by the user when reviewing the new regexes.  Variable terms are
        replaced by \texttt{.+}, which means to match zero or more of any
        character.

@@

\begin{eqlist}[\def\makelabel#1{\bfseries#1:}]

    \squeezeitems{}

@@

Some mail clients disconnect abruptly if a second or subsequent recipient
is rejected; they may also disconnect after other errors, but such
disconnections are either unimportant or are handled elsewhere in the
parser (\sectionref{timeouts-during-data-phase}).  Sadly, Postfix does not
log a message saying the mail has been discarded, as should be expected by
now.  The checks to identify this happening are:

@@

    \item The hostname used in the HELO command is not logged if the mail
        is accepted.  Rectifying this is relatively simple: create a
        restriction that is guaranteed to warn for every accepted mail, as
        follows:
